Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-11-30 article.tex
Removed extra space
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1422 ccdd05d5-56c1-461a-bf98-85f6876523b4
Not counterclockwise
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1425 ccdd05d5-56c1-461a-bf98-85f6876523b4

	\caption{\label{fig:low-frequency-cutoff}Counterclockwise from top left:  (a)~Noise amplitude spectral density for a variety of Advanced LIGO noise models, S5, and S6.  (b)~Normalized signal to noise per unit frequency, $(\mathrm{d}\rho^2/\mathrm{d}f)/\rho^2$, for a (1.4,~1.4)~$\Msun$ inspiral.  (c)~Percentage of SNR that is accumulated from $f_\mathrm{low}$ to $f_\mathrm{ISCO}$, relative to SNR accumulated from $f_\mathrm{low} = 0\,\mathrm{Hz}$ to $f_\mathrm{ISCO}$.    (d)~Amount of time for a \NS--\NS\ inspiral signal to evolve from frequency $f_\mathrm{low}$ to $f_\mathrm{ISCO}$, as a function of $f_\mathrm{low}$.  For figures (a) through (c), the line style indicates which noise model was used.}
\end{figure}

>>>>

	\caption{\label{fig:low-frequency-cutoff}From top left:  (a)~Noise amplitude spectral density for a variety of Advanced LIGO noise models, S5, and S6.  (b)~Normalized signal to noise per unit frequency, $(\mathrm{d}\rho^2/\mathrm{d}f)/\rho^2$, for a (1.4,~1.4)~$\Msun$ inspiral.  (c)~Percentage of SNR that is accumulated from $f_\mathrm{low}$ to $f_\mathrm{ISCO}$, relative to SNR accumulated from $f_\mathrm{low} = 0\,\mathrm{Hz}$ to $f_\mathrm{ISCO}$.    (d)~Amount of time for a \NS--\NS\ inspiral signal to evolve from frequency $f_\mathrm{low}$ to $f_\mathrm{ISCO}$, as a function of $f_\mathrm{low}$.  For figures (a) through (c), the line style indicates which noise model was used.}
\end{figure}
